COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries

### 2021-06-22 paper_files/figure-latex/histcattrust-1.tex
update

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:14
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
	(371.71,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
	(371.71,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
	(371.71,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
	(371.71,619.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
	(371.71,551.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
	(371.71,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
	(371.71,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
	(371.71,609.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
	( 75.24,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
	(120.16,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
	(165.08,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
	(209.99,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
	(254.91,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
	(299.83,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
	(344.75,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);

\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);

\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);

\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);

\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);

\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);

\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);

\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);

\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);

\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);

\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);

\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);

\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);

\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);

\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);

\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);

\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);

\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);

\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
	(371.71,475.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
	(371.71,494.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
	(371.71,514.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
	(371.71,533.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
	(371.71,465.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
	(371.71,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
	(371.71,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
	(371.71,523.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
	( 75.24,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
	(120.16,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
	(165.08,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
	(209.99,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
	(254.91,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
	(299.83,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
	(344.75,542.14);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);

\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);

\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);

\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);

\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);

\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);

\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);

\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);

\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);

\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);

\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);

\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);

\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);

\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);

\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);

\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);

\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);

\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
	(371.71,389.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
	(371.71,409.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
	(371.71,428.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
	(371.71,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
	(371.71,380.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
	(371.71,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
	(371.71,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
	(371.71,438.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
	( 75.24,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
	(120.16,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
	(165.08,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
	(209.99,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
	(254.91,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
	(299.83,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
	(344.75,456.51);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);

\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);

\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);

\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);

\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);

\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);

\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);

\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);

\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);

\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);

\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);

\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);

\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);

\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);

\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);

\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);

\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);

\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
	(371.71,304.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
	(371.71,323.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
	(371.71,342.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
	(371.71,362.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
	(371.71,294.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
	(371.71,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
	(371.71,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
	(371.71,352.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
	( 75.24,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
	(120.16,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
	(165.08,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
	(209.99,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
	(254.91,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
	(299.83,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
	(344.75,370.88);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);

\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);

\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);

\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);

\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);

\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);

\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);

\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);

\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);

\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);

\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);

\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
	(371.71,218.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
	(371.71,237.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
	(371.71,257.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
	(371.71,276.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
	(371.71,208.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
	(371.71,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
	(371.71,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
	(371.71,266.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
	( 75.24,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
	(120.16,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
	(165.08,285.25);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:47
% !TEX encoding = UTF-8 Unicode
% !TEX program = xelatex

\documentclass[fontsize=7pt,DIV=calc]{scrartcl}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,548.04) rectangle (369.36,631.27);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,548.04) rectangle (369.36,631.27);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,561.87) --
	(369.36,561.87);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,581.98) --
	(369.36,581.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,602.08) --
	(369.36,602.08);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,622.18) --
	(369.36,622.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,551.82) --
	(369.36,551.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,571.92) --
	(369.36,571.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,592.03) --
	(369.36,592.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,612.13) --
	(369.36,612.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,548.04) --
	( 68.60,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,548.04) --
	(114.17,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,548.04) --
	(159.74,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,548.04) --
	(205.31,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,548.04) --
	(250.88,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,548.04) --
	(296.45,631.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,548.04) --
	(342.02,631.27);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (166.57,551.82) rectangle (180.24,566.62);

\path[fill=fillColor] (257.71,551.82) rectangle (271.38,553.35);

\path[fill=fillColor] (212.14,551.82) rectangle (225.81,553.27);

\path[fill=fillColor] (303.28,551.82) rectangle (316.95,561.15);

\path[fill=fillColor] (348.85,551.82) rectangle (362.52,553.19);

\path[fill=fillColor] ( 75.43,551.82) rectangle ( 89.10,593.31);

\path[fill=fillColor] (121.00,551.82) rectangle (134.67,562.20);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (152.90,551.82) rectangle (166.57,567.58);

\path[fill=fillColor] (244.04,551.82) rectangle (257.71,553.43);

\path[fill=fillColor] (198.47,551.82) rectangle (212.14,552.55);

\path[fill=fillColor] (289.61,551.82) rectangle (303.28,555.68);

\path[fill=fillColor] (335.18,551.82) rectangle (348.85,552.14);

\path[fill=fillColor] ( 61.76,551.82) rectangle ( 75.43,597.74);

\path[fill=fillColor] (107.33,551.82) rectangle (121.00,563.96);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (139.23,551.82) rectangle (152.90,564.85);

\path[fill=fillColor] (230.37,551.82) rectangle (244.04,553.11);

\path[fill=fillColor] (184.80,551.82) rectangle (198.47,554.80);

\path[fill=fillColor] (275.94,551.82) rectangle (289.61,572.01);

\path[fill=fillColor] (321.51,551.82) rectangle (335.18,555.20);

\path[fill=fillColor] ( 48.09,551.82) rectangle ( 61.76,584.55);

\path[fill=fillColor] ( 93.66,551.82) rectangle (107.33,558.66);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,548.04) rectangle (369.36,631.27);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,459.31) rectangle (369.36,542.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,459.31) rectangle (369.36,542.54);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,473.14) --
	(369.36,473.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,493.25) --
	(369.36,493.25);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,513.35) --
	(369.36,513.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,533.45) --
	(369.36,533.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,463.09) --
	(369.36,463.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,483.19) --
	(369.36,483.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,503.30) --
	(369.36,503.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,523.40) --
	(369.36,523.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,459.31) --
	( 68.60,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,459.31) --
	(114.17,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,459.31) --
	(159.74,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,459.31) --
	(205.31,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,459.31) --
	(250.88,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,459.31) --
	(296.45,542.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,459.31) --
	(342.02,542.54);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (166.57,463.09) rectangle (180.24,491.72);

\path[fill=fillColor] (250.88,463.09) rectangle (271.38,463.41);

\path[fill=fillColor] (212.14,463.09) rectangle (225.81,476.04);

\path[fill=fillColor] (303.28,463.09) rectangle (316.95,463.49);

\path[fill=fillColor] (348.85,463.09) rectangle (362.52,465.02);

\path[fill=fillColor] ( 75.43,463.09) rectangle ( 89.10,498.63);

\path[fill=fillColor] (121.00,463.09) rectangle (134.67,463.74);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (152.90,463.09) rectangle (166.57,492.20);

\path[fill=fillColor] (230.37,463.09) rectangle (250.88,463.41);

\path[fill=fillColor] (198.47,463.09) rectangle (212.14,476.04);

\path[fill=fillColor] (289.61,463.09) rectangle (303.28,463.49);

\path[fill=fillColor] (335.18,463.09) rectangle (348.85,464.14);

\path[fill=fillColor] ( 61.76,463.09) rectangle ( 75.43,499.03);

\path[fill=fillColor] (107.33,463.09) rectangle (121.00,463.65);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (139.23,463.09) rectangle (152.90,478.13);

\path[fill=fillColor] (184.80,463.09) rectangle (198.47,476.60);

\path[fill=fillColor] (275.94,463.09) rectangle (289.61,463.90);

\path[fill=fillColor] (321.51,463.09) rectangle (335.18,488.18);

\path[fill=fillColor] ( 48.09,463.09) rectangle ( 61.76,487.38);

\path[fill=fillColor] ( 93.66,463.09) rectangle (107.33,464.78);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,459.31) rectangle (369.36,542.54);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,370.58) rectangle (369.36,453.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,370.58) rectangle (369.36,453.81);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,384.41) --
	(369.36,384.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,404.51) --
	(369.36,404.51);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,424.62) --
	(369.36,424.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,444.72) --
	(369.36,444.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,374.36) --
	(369.36,374.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,394.46) --
	(369.36,394.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,414.57) --
	(369.36,414.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,434.67) --
	(369.36,434.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,370.58) --
	( 68.60,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,370.58) --
	(114.17,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,370.58) --
	(159.74,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,370.58) --
	(205.31,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,370.58) --
	(250.88,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,370.58) --
	(296.45,453.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,370.58) --
	(342.02,453.81);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (166.57,374.36) rectangle (180.24,386.42);

\path[fill=fillColor] (250.88,374.36) rectangle (271.38,374.84);

\path[fill=fillColor] (212.14,374.36) rectangle (225.81,375.25);

\path[fill=fillColor] (303.28,374.36) rectangle (316.95,401.06);

\path[fill=fillColor] (348.85,374.36) rectangle (362.52,374.68);

\path[fill=fillColor] ( 75.43,374.36) rectangle ( 89.10,392.86);

\path[fill=fillColor] (121.00,374.36) rectangle (134.67,395.83);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (152.90,374.36) rectangle (166.57,386.50);

\path[fill=fillColor] (230.37,374.36) rectangle (250.88,374.92);

\path[fill=fillColor] (198.47,374.36) rectangle (212.14,375.17);

\path[fill=fillColor] (289.61,374.36) rectangle (303.28,400.09);

\path[fill=fillColor] (335.18,374.36) rectangle (348.85,374.44);

\path[fill=fillColor] ( 61.76,374.36) rectangle ( 75.43,393.50);

\path[fill=fillColor] (107.33,374.36) rectangle (121.00,396.39);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (139.23,374.36) rectangle (152.90,384.65);

\path[fill=fillColor] (184.80,374.36) rectangle (198.47,376.69);

\path[fill=fillColor] (275.94,374.36) rectangle (289.61,417.14);

\path[fill=fillColor] (321.51,374.36) rectangle (335.18,378.78);

\path[fill=fillColor] ( 48.09,374.36) rectangle ( 61.76,382.48);

\path[fill=fillColor] ( 93.66,374.36) rectangle (107.33,386.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,370.58) rectangle (369.36,453.81);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,281.85) rectangle (369.36,365.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,281.85) rectangle (369.36,365.08);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,295.68) --
	(369.36,295.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,315.78) --
	(369.36,315.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,335.89) --
	(369.36,335.89);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,355.99) --
	(369.36,355.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,285.63) --
	(369.36,285.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,305.73) --
	(369.36,305.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,325.84) --
	(369.36,325.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,345.94) --
	(369.36,345.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,281.85) --
	( 68.60,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,281.85) --
	(114.17,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,281.85) --
	(159.74,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,281.85) --
	(205.31,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,281.85) --
	(250.88,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,281.85) --
	(296.45,365.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,281.85) --
	(342.02,365.08);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (166.57,285.63) rectangle (180.24,288.12);

\path[fill=fillColor] (250.88,285.63) rectangle (271.38,285.63);

\path[fill=fillColor] (212.14,285.63) rectangle (225.81,287.00);

\path[fill=fillColor] (303.28,285.63) rectangle (316.95,290.29);

\path[fill=fillColor] ( 75.43,285.63) rectangle ( 89.10,357.44);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (152.90,285.63) rectangle (166.57,288.04);

\path[fill=fillColor] (230.37,285.63) rectangle (250.88,285.71);

\path[fill=fillColor] (198.47,285.63) rectangle (212.14,286.35);

\path[fill=fillColor] (289.61,285.63) rectangle (303.28,287.16);

\path[fill=fillColor] ( 61.76,285.63) rectangle ( 75.43,361.30);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (139.23,285.63) rectangle (152.90,288.77);

\path[fill=fillColor] (184.80,285.63) rectangle (198.47,291.66);

\path[fill=fillColor] (275.94,285.63) rectangle (289.61,312.89);

\path[fill=fillColor] ( 48.09,285.63) rectangle ( 61.76,329.61);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,281.85) rectangle (369.36,365.08);
\end{scope}
\begin{scope}
\path[clip] ( 41.25,193.12) rectangle (369.36,276.35);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 41.25,193.12) rectangle (369.36,276.35);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,206.95) --
	(369.36,206.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,227.05) --
	(369.36,227.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,247.16) --
	(369.36,247.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,267.26) --
	(369.36,267.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,196.90) --
	(369.36,196.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,217.00) --
	(369.36,217.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,237.10) --
	(369.36,237.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,257.21) --
	(369.36,257.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,193.12) --
	( 68.60,276.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,193.12) --
	(114.17,276.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,193.12) --
	(159.74,276.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,193.12) --
	(205.31,276.35);
